 

### 2020-09-09 tables.Rmd
one more fix

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
metabolism_table <- read.csv("Lit_Review/metabolism_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(metabolism_table, caption = "Table 2. Summary of observed variation in leaf metabolism and thermal responses across the vertical gradient and/or between sun and shade leaves", format = "latex", booktabs = TRUE,  escape = F)%>%
  column_spec(1, width = "6cm") %>%
  column_spec(2, width = "2cm") %>%
  column_spec(6, width = "4cm") %>%
  pack_rows("Stomatal conductance", 1, 7, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Photosynthesis", 8, 20, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Respiration", 21, 27, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("VOC production", 28, 29, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) 
  #NOTE: REFERENCES for this table need to go in the nocite section of header in the main doc!!!
```
*composite climatic stress variable from canopy temperature, vapour pressure deficit, and relative humidity is higher in lower canopy

>>>>

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
metabolism_table <- read.csv("Lit_Review/metabolism_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(metabolism_table, caption = "Table 2. Summary of observed variation in leaf metabolism and thermal responses across the vertical gradient and/or between sun and shade leaves", format = "latex", booktabs = TRUE,  escape = F)%>%
  column_spec(1, width = "6cm") %>%
  column_spec(2, width = "2cm") %>%
  column_spec(6, width = "4cm") %>%
  pack_rows("Stomatal conductance", 1, 7, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Photosynthesis", 8, 20, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Respiration", 21, 28, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("VOC production", 29, 30, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) 
  #NOTE: REFERENCES for this table need to go in the nocite section of header in the main doc!!!
```
*composite climatic stress variable from canopy temperature, vapour pressure deficit, and relative humidity is higher in lower canopy
